---
output:
  html_document:
    number_sections: TRUE
    toc: true
#    toc_float: true
    toc_depth: 2
    fig_width: 9
    fig_height: 7
    fig_caption: true
    includes:
      after_body: footer.html
params:
  title:
  current_file:
  previous_file:
  individual_plots: TRUE
  filter_outliers: FALSE
title: "`r params$title`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(conflicts.policy = list(error = FALSE, warn = FALSE))

source("fastfile.r")
library(knitr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(forcats)
library(hrbrthemes)
library(viridis)
library(scales)
library(gdata, include.only=c("humanReadable"))

current_color <- "#56B4E9"
previous_color <- "#B12729"

has_previous <- !is.null(params$previous_file)
is_filter_outliers <- params$filter_outliers
```

```{r reading_results}
current <- load_results(params$current_file)
if (is_filter_outliers) {
  filtered <- filter_outliers(current, 3)
  current_filtered <- nrow(current) - nrow(filtered)
  current <- filtered
}

# If we are in comparision mode
previous <- if (has_previous) { load_results(params$previous_file) }
if (has_previous && is_filter_outliers) {
  filtered <- filter_outliers(previous, 3)
  previous_filtered <- nrow(previous) - nrow(filtered)
  previous <- filtered
}

```



# Overview

```{r overview}
p <- plot(title="Run time PDF per file size", xlab="File Size", ylab="Run Time [ms]") +
    scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format(function(x) x, function(x) round(x, digits=2))) +
    coord_flip() # This switch X and Y axis and allows to get the horizontal version
if (has_previous) {
  p <- p +
    geom_violin(data=previous, aes(x=file_size_human, y=time), fill=previous_color, color=previous_color, alpha=0.8)
}
p +
  geom_violin(data=current, aes(x=file_size_human, y=time), fill=current_color, color=current_color, alpha=0.8)

```

This analysis has been run `r Sys.time()`.

Showing benchmark results for "_`r params$current_file`_" with `r if (is_filter_outliers) { sprintf("%d (%d filtered)", nrow(current), current_filtered) } else { sprintf("%d", nrow(current)) }` samples.  
`r if (has_previous) {
  if (is_filter_outliers) {
    sprintf("Comparing with results from _%s_ with %d (%d filtered) samples.", params$previous_file, nrow(previous), previous_filtered)
  } else {
    sprintf("Comparing with results from _%s_ with %d samples.", params$previous_file, nrow(previous))
  }
}`



# Mean and Median Run Time

```{r meanruntime, out.width=c('50%', '50%'), fig.show='hold'}
# Mean
current_means <- aggregate_results(current, mean)
previous_means <- if (has_previous) { aggregate_results(previous, mean) }

p <- plot(title="Mean runtime", xlab="File Size", ylab="median Run Time [ms]") +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format(function(x) x, function(x) hr(x))) +
    scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format(function(x) x, function(x) round(x, digits=2)))
if (has_previous) {
  p <- p + 
    geom_segment(data=previous_means, mapping=aes(x=file_size, y=time, xend=c(tail(file_size, n=-1), NA), yend=c(tail(time, n=-1), NA)), alpha=0.8, color=previous_color) +
    geom_point(data=previous_means, aes(x=file_size, y=time), shape=21, color="black", fill=previous_color, alpha=0.8, size=3)
}
p +
  geom_segment(data=current_means, mapping=aes(x=file_size, y=time, xend=c(tail(file_size, n=-1), NA), yend=c(tail(time, n=-1), NA)), color=current_color) +
  geom_point(data=current_means, aes(x=file_size, y=time), shape=21, color="black", fill=current_color, size=3)

# Median
current_medians <- aggregate_results(current, median)
previous_medians <- if (has_previous) { aggregate_results(previous, median) }

p <- plot(title="Median runtime", xlab="File Size", ylab="median Run Time [ms]") +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format(function(x) x, function(x) hr(x))) +
    scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format(function(x) x, function(x) round(x, digits=2)))
if (has_previous) {
  p <- p + 
    geom_segment(data=previous_medians, mapping=aes(x=file_size, y=time, xend=c(tail(file_size, n=-1), NA), yend=c(tail(time, n=-1), NA)), alpha=0.8, color=previous_color) +
    geom_point(data=previous_medians, aes(x=file_size, y=time), shape=21, color="black", fill=previous_color, alpha=0.8, size=3)
}
p  +
  geom_segment(data=current_medians, mapping=aes(x=file_size, y=time, xend=c(tail(file_size, n=-1), NA), yend=c(tail(time, n=-1), NA)), color=current_color) +
  geom_point(data=current_medians, aes(x=file_size, y=time), shape=21, color="black", fill=current_color, size=3)
```



`r if (has_previous) { "## Mean and Median Speed Up" }`
```{r meanspeedup, eval = has_previous, out.width=c('50%', '50%'), fig.show='hold'}

speedups_stats <- if (is_filter_outliers) {
  calc_speedups_wo_outliers(current, previous)
} else {
  calc_speedups(current, previous)
}

speedups_stats

# Mean with Standard Error
if (is_filter_outliers) {
  conditional_coloring_plot(title="Mean Speedup", xlab="File Size", ylab="Speed Up in %") +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format(function(x) x, function(x) hr(x))) +
    geom_bar(data=speedups_stats, aes(x=file_size, y=mean, fill=mean < 0), stat="identity", alpha=0.8)
} else {
  conditional_coloring_plot(title="Mean Speedup with Std Error", xlab="File Size", ylab="Speed Up in %") +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format(function(x) x, function(x) hr(x))) +
    geom_bar(data=speedups_stats, aes(x=file_size, y=mean, fill=mean < 0), stat="identity", alpha=0.8) +
    geom_errorbar(data=speedups_stats, aes(x=file_size, ymin=mean-sd, ymax=mean+sd, color=mean < 0), width=0.4, alpha=0.9, size=0.5)
}

# Median
conditional_coloring_plot(title="Median Speedup", xlab="File Size", ylab="Speed Up in %") +
  scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format(function(x) x, function(x) hr(x))) +
  geom_bar(data=speedups_stats, aes(x=file_size, y=median, fill=median < 0), stat="identity", alpha=0.8)
```




`r if (params$individual_plots) { "# Run Time for Individual File Sizes" }`
```{r individual_computation, eval = params$individual_plots}
rmd <- sapply(
  unique(current$file_size),
  function(x) {
    knit_expand(file="individual.tmpl.rmd", file_size=x)
  }
)
rmd <- paste(rmd, collapse = "\n")
```  
```{r individual_output, results="asis", eval = params$individual_plots} 
rendered <- knit(text=rmd, quiet=TRUE) 
cat(rendered, sep="\n") 
``` 
